---
title: "BrainCellularComposition User Guide"
shorttitle: "BrainCellularComposition guide"
output: rmarkdown::html_vignette
fig_width: 8
fig_height: 6
vignette: >
  %\VignetteIndexEntry{BrainCellularComposition}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installation 

From Bioconductor 

```{r, eval = FALSE}
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
BiocManager::install("BrainCellularComposition")
```

Development version can be installed from GitHub


# Introduction

The `BrainCellularComposition` package provides gene expression data for purified brain cell-types as collated and benchmarked in Sutton et al. (2021). 

The `sigsBrain` data object contains the following signatures: 

* F5: Cultured cells obtained from the FANTOM5 consortium containing only neuron and astrocyte cell-type composition for each gene 

* IP: Immunopurified whole-cells from the human cortex from Zhang et al (2016)

* MM: Immunopurified whole-cells from the mouse cortex from Zhang et al (2015)

* CA: Single-nucleus RNA-sequencing of post-mortem human brain from the Human Cell Atlas 

* LK: Single-nucleus RNA-sequencing of the post-mortem human adult frontal cortex from Lake et al (2018)  

* TS: Single-cell RNA-sequencing from the adult mouse cortex from Tasic et al () 

* NG: Single-nucleus RNA-sequencing from the adult human post-mortem prefrontal cortex from Nagy et al 

* DM: Single-cell nucleus RNA-sequencing from the muddle temporal gyrus generated by Darmanis et al (2015) 

* VL: Single-nucleus RNA-sequencing of post-mortem adult human brain from Velmeshev et al

* MB: Multibrain signature generated by quantile-normalising and averaging RPKM expression levels of CA, IP, DM, NG and VL signatures


# Usage 



```{r setup}
library(BrainCellularComposition)
library(ExperimentHub)
```


For example to retrieve neurons from the F5 dataset 

```{r, eval = TRUE}
F5_neurons <- loadSignature("F5", "Neurons")
```
